Limited information strategies for topological games

### 2015-03-11 phd/talks-and-presentations/2015-03-11-defense.tex
Fix bmgame typos

\newcommand{\bmGame}[1]{{BM}_{N,E}(#1)}

@@

  The first player $\pl N$ wins the game if the intersection of all the chosen
  open sets is nonempty.
  \end{game}
\end{frame}

\begin{frame}
  \begin{theorem}
    $X$ is Baire if and only if $\pl N$ lacks a winning strategy
    in the Banach Mazur game ($\pl N\not\win\bmGame{X}$).
  \end{theorem}

@@

  \begin{theorem}
    $X$ is $\alpha$-favorable $\Rightarrow$
    $X$ is weakly $\alpha$-favorable $\Rightarrow$
    $X$ is Baire
  \end{theorem}

@@

  $\alpha$-favorability is characterized by $\pl E\tactwin\bmGame{X}$:
  player $\pl E$ has a \term{tactical} winning strategy which only considers
  the most recent move of the opponent.

@@

  This is stronger than weak
  $\alpha$-favorability \cite{MR817083}, characterized by $\pl E\win\bmGame{X}$.
  In this case $\pl E$ still has a winning strategy, but it may
  rely on perfect information of the history of the game.
\end{frame}

>>>>

\newcommand{\bmGame}[1]{{BM}_{E,N}(#1)}

@@

  The first player $\pl E$ wins the game if the intersection of all the chosen
  open sets is empty.
  \end{game}
\end{frame}

\begin{frame}
  \begin{theorem}
    $X$ is Baire if and only if $\pl E$ lacks a winning strategy
    in the Banach Mazur game ($\pl E\not\win\bmGame{X}$).
  \end{theorem}

@@

  \begin{theorem}
    $X$ is $\alpha$-favorable $\Rightarrow$
    $X$ is Choquet $\Rightarrow$
    $X$ is Baire
  \end{theorem}

@@

  $\alpha$-favorability is characterized by $\pl N\tactwin\bmGame{X}$:
  player $\pl E$ has a \term{tactical} winning strategy which only considers
  the most recent move of the opponent.

@@

  This is stronger than the Choquet property \cite{MR817083},
  characterized by $\pl N\win\bmGame{X}$.
  In this case $\pl N$ still has a winning strategy, but it may
  rely on perfect information of the history of the game.
\end{frame}
